---
title: "Ex-post Evidence"
author: "Joe Raymond"
date: "`r Sys.Date()`"
output: pdf_document
---

## Evidence for ex-post diversity selection bias

One of the problems with using ex-post measures of diversification and revenue uncertainty is that a boat may only look diversified in the data during a "good" or "bad" fishing season. That is, there may be correlation between the likelihood of a boat obtaining below average revenue 

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(warning = TRUE, message = TRUE)

{packs <- c('readr', 'tidyverse', 'dplyr', 'ggplot2', 'xlsx','data.table', 'fixest', 'lubridate', 'corrplot', 'RColorBrewer', 'knitr', 'cluster','factoextra', 'zoo', 'purrr')
  new.packages <- packs[!(packs %in% installed.packages()[,"Package"])]
  if(length(new.packages)) install.packages(new.packages)
  lapply(packs, require, character.only = T)}#probably could just use loadpacks but this should work

setwd("/home/akfin/jraymond/Rprojects/joe-thesis")
source("code/myfunctions.R")

setwd("/home/akfin/jraymond/Rprojects/joe-thesis")
{
  load("intermediate data/catch_data_temp.rdata")
  #catch_data_temp %>% ungroup %>% group_by(Vessel.ADFG.Number) %>% filter(any(substr(CFEC.Permit.Fishery, 1, 1) == "S")) %>% nrow()#this filter would filter to jsut the boats that have fished salmon permit at some point
  catch_data_temp$Vessel.ADFG.Number[which(catch_data_temp$Vessel.ADFG.Number==62.39)] <- 62339#fix a typo in the data
  catch_data_temp <- catch_data_temp %>% filter(Vessel.ADFG.Number!=0) #8 missing values with vessel numbers == 0
  catch_data_temp <- catch_data_temp %>% mutate(Vessel.ADFG.Number = as.integer(Vessel.ADFG.Number))
  catch_data_temp <- catch_data_temp %>% mutate(CFEC.Value..Detail. = if_else(is.na(CFEC.Value..Detail.),0,CFEC.Value..Detail.))
  #filter out boats that made landings but did not report the permit/fishery in which they made the landing
  catch_data_temp <- catch_data_temp %>% group_by(Vessel.ADFG.Number, Batch.Year) %>% filter(!any(is.na(Permit.Serial.Number)) ) %>% ungroup()
}

{
  trip.data <- get.trip(catch_data_temp)
  trip.data$trip.duration <- as.numeric(trip.data$trip.length)+1
  trip.data <- trip.data %>% mutate(trip.duration=ifelse(trip.duration>0,trip.duration, NA))#going out and back the same day should lead to trip duration = 1
}
{
  permit.annual.rev <- trip.data %>% 
    group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number, Vessel.ADFG.Number, CFEC.Permit.Serial.Number) %>% 
    summarise(year.revenue=sum(CFEC.Value..Detail., na.rm = TRUE), 
              num.trips = n_distinct(trip.id), 
              fishing.days = sum(trip.duration, na.rm = TRUE), 
              unique.checks = n_distinct(CFEC.Permit.Check), 
              CFEC.Permit.Check = first(CFEC.Permit.Check), 
              max.seq.num = max(CFEC.Permit.Sequence), 
              CFEC.Vessel.Owner.Filing.Number = ifelse(all(is.na(CFEC.Vessel.Owner.Filing.Number)), NA, first(na.omit(CFEC.Vessel.Owner.Filing.Number))), 
              CFEC.Permit.Fishery = ifelse(all(is.na(CFEC.Permit.Fishery)), NA, first(na.omit(CFEC.Permit.Fishery)))) %>% 
    mutate(revenue.per.trip = year.revenue/(num.trips))
  
  rm(catch_data_temp)
  gc()
}  
period_length <- 10
```

```{r first permit deviations}
get.owner.ppermit <- function(df){ #gets the first permit for each owner-year; picking the permit for each vessel that has the most revenue in a given year
  df_test <- df %>% ungroup() %>%  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number, CFEC.Permit.Fishery) %>% summarise(tot.revenue = sum(year.revenue, na.rm = TRUE)) %>%
    filter(CFEC.Permit.Fishery!="") %>% 
    group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
    summarise(first.permit = CFEC.Permit.Fishery[first(which(tot.revenue==max(tot.revenue)))], second.permit = ifelse(length(unique(CFEC.Permit.Fishery))==1, NA, CFEC.Permit.Fishery[first(which(tot.revenue==second_max(tot.revenue)))]), permit.fished.max = length(unique(CFEC.Permit.Fishery)))#second_max() is a function from myfunctions.r and it returns the second highest value if it exists (NA otherwise)
  return(df_test)
}

#first.permit.df <- get.owner.ppermit(permit.annual.rev)


rev.permits.changing <- permit.annual.rev %>% ungroup() %>%
  group_by(CFEC.Permit.Holder.Filing.Number, Batch.Year, CFEC.Permit.Fishery) %>% 
  summarise(fishery.annual.rev = sum(year.revenue, na.rm = TRUE)) %>%
  ungroup() %>% mutate(period = floor((Batch.Year - 1991) / period_length) + 1) %>% 
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  mutate(owner.annual.rev = sum(fishery.annual.rev, na.rm = TRUE), annual.rev.share = fishery.annual.rev/sum(fishery.annual.rev, na.rm = TRUE), owner.annual.hhi = sum(annual.rev.share^2, na.rm = TRUE)) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  mutate(period.avg.owner.rev = mean(owner.annual.rev, na.rm = TRUE)) %>%
  group_by(CFEC.Permit.Holder.Filing.Number, Batch.Year) %>% 
  mutate(owner.rev.dev = owner.annual.rev-period.avg.owner.rev) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, period, CFEC.Permit.Fishery) %>% 
  mutate(period.avg.rev = mean(fishery.annual.rev, na.rm = TRUE), period.rev.share = period.avg.rev/period.avg.owner.rev) %>%
  group_by(CFEC.Permit.Holder.Filing.Number, Batch.Year, CFEC.Permit.Fishery) %>% 
  mutate(permit.rev.deviation = (fishery.annual.rev - period.avg.rev)) %>% 
  filter(!is.na(CFEC.Permit.Holder.Filing.Number)) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, Batch.Year) %>%
  mutate(is.prime.permit = if_else(fishery.annual.rev == max(fishery.annual.rev), 1,0))

#variable to tell if the largest shock in a owner-year was caused by a primary permit shock or not
rev.permits.changing <- rev.permits.changing %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, Batch.Year) %>% 
  mutate(is.biggest.change = if_else(abs(permit.rev.deviation) == max(abs(permit.rev.deviation), na.rm = TRUE), 1,0), 
         is.shock.pp = (is.biggest.change*is.prime.permit)) %>% 
  group_by(period, CFEC.Permit.Holder.Filing.Number) %>% 
  mutate(period.avg.hhi = mean(owner.annual.hhi, na.rm = TRUE)) %>% 
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  arrange(Batch.Year) %>% 
  mutate(hhi.deviation = owner.annual.hhi - period.avg.hhi, rev.deviation = (owner.annual.rev - period.avg.rev)/period.avg.rev)# calculate change in hhi from the period mean

rev.permits.changing <- rev.permits.changing %>%
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  mutate(period.share.sum = sum(annual.rev.share)) %>% #summing up the revenue from the entire period for each permit holder
  group_by(CFEC.Permit.Holder.Filing.Number, period, CFEC.Permit.Fishery) %>% 
  mutate(fishery.share.share = sum(annual.rev.share, na.rm = TRUE)/period.share.sum)



# calculating the "overall" period-level hhi (versus averaging the annual hhi's)
tenyear.owner.permits <- rev.permits.changing %>% ungroup() %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  mutate(period.owner.tot.rev = sum(fishery.annual.rev, na.rm =TRUE)) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, period, CFEC.Permit.Fishery) %>% 
  summarise(period.total.share = sum(fishery.annual.rev, na.rm = TRUE)/first(period.owner.tot.rev), fishery.share.share = first(fishery.share.share), period.share.sum = first(period.share.sum), AnnualAverageHHI = first(period.avg.hhi)) %>%
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  mutate(period.owner.tot.hhi = sum(period.total.share^2, na.rm = TRUE), norm.period.hhi = sum(fishery.share.share^2, na.rm = TRUE), period.hhi.diff = period.owner.tot.hhi-norm.period.hhi)

rev.permits.changing <- rev.permits.changing %>% 
  left_join(tenyear.owner.permits, join_by(CFEC.Permit.Holder.Filing.Number, period, CFEC.Permit.Fishery)) %>% 
  mutate(norm.hhi.diff = norm.period.hhi-period.avg.hhi, hhi.diff = period.owner.tot.hhi-period.avg.hhi)


  
rev.permits.changing %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S") %>% 
  ggplot(aes()) +
  geom_density(aes(x = period.avg.hhi, fill = "Annual Average"), alpha = 0.6) +
    geom_density(aes(x = norm.period.hhi, fill = "Norm Period Agggregate"), alpha = 0.4) +
  geom_density(aes(x = period.owner.tot.hhi, fill = "Period Agggregate"), alpha = 0.4) +
  facet_wrap(~ CFEC.Permit.Fishery, scales = "free") +
  labs(title = "Density Plots of Annual Average HHI, Period Agggregate HHI, and Norm Period Agggregate HHI",
       x = "hhi value",
       y = "Density") +
  theme_minimal()+
  scale_fill_manual(name = "", values = c("Annual Average" = "red", "Period Agggregate" = "blue2", "Norm Period Agggregate" = "green4"))

rev.permits.changing %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S", period==1) %>% 
  ggplot(aes()) +
  geom_density(aes(x = period.avg.hhi, fill = "Annual Average"), alpha = 0.6) +
    geom_density(aes(x = norm.period.hhi, fill = "Norm Period Agggregate"), alpha = 0.4) +
  geom_density(aes(x = period.owner.tot.hhi, fill = "Period Agggregate"), alpha = 0.4) +
  facet_wrap(~ CFEC.Permit.Fishery, scales = "free") +
  labs(title = "(1990-2000) Density Plots of Annual Average HHI, Period Agggregate HHI, and Norm Period Agggregate HHI",
       x = "hhi value",
       y = "Density") +
  theme_minimal()+
  scale_fill_manual(name = "", values = c("Annual Average" = "red", "Period Agggregate" = "blue2", "Norm Period Agggregate" = "green4"))



rev.permits.changing %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S") %>% ggplot(aes(x = hhi.diff)) +
  geom_density(fill="steelblue4", alpha = 0.8) +
  facet_wrap(~ CFEC.Permit.Fishery, scales = "free") +
  labs(title = "Density Plots of (Period-Aggregate HHI) - (Average Annual HHI) ",
       x = "hhi.diff",
       y = "Density") +
  theme_minimal()

rev.permits.changing %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S") %>% ggplot(aes()) +
  geom_density(aes(x = period.hhi.diff), fill="steelblue4", alpha = 0.8) +
  facet_wrap(~ CFEC.Permit.Fishery, scales = "free") +
  labs(title = "Density Plots of (Period Agggregate HHI) - (Norm Period Agggregate HHI) ",
       x = "hhi.diff",
       y = "Density") +
  theme_minimal()

rev.permits.changing %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S") %>% ggplot(aes()) +
  geom_density(aes(x = hhi.diff), fill="steelblue4", alpha = 0.8) +
  facet_wrap(~ CFEC.Permit.Fishery, scales = "free") +
  labs(title = "Density Plots of (Period Agggregate HHI) - (Norm Period Agggregate HHI) ",
       x = "hhi.diff",
       y = "Density") +
  theme_minimal()

rev.permits.changing %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S") %>% ggplot(aes(x = hhi.diff)) +
  geom_density() +
  facet_wrap(~ CFEC.Permit.Fishery, scales = "free") +
  labs(title = "Density Plots of hhi.diff by CFEC.Permit.Fishery",
       x = "hhi.diff",
       y = "Density") +
  theme_minimal()

rev.permits.changing %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S") %>% ggplot(aes(x = hhi.diff)) +
  geom_density() +
  facet_wrap(~ CFEC.Permit.Fishery, scales = "free") +
  labs(title = "Density Plots of hhi.diff by CFEC.Permit.Fishery",
       x = "hhi.diff",
       y = "Density") +
  theme_minimal()

### Scatter Plots

tenyear.owner.permits %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S", period==1) %>% 
  ggplot() +
  geom_point(aes(x = AnnualAverageHHI, y = period.owner.tot.hhi)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(title = "(1990-2000) Annual Average HHI (x), Period Agggregate HHI (y)",
       x = "Annual Average HHI",
       y = "Period Agggregate HHI") +
  theme_minimal()

tenyear.owner.permits %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S", period==2) %>% 
  ggplot() +
  geom_point(aes(x = AnnualAverageHHI, y = period.owner.tot.hhi)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(title = "(2000-2010) Annual Average HHI (x), Period Agggregate HHI (y)",
       x = "Annual Average HHI",
       y = "Period Agggregate HHI") +
  theme_minimal()

tenyear.owner.permits %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S", period==3) %>% 
  ggplot() +
  geom_point(aes(x = AnnualAverageHHI, y = period.owner.tot.hhi)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(title = "(2010-2020) Annual Average HHI (x), Period Agggregate HHI (y)",
       x = "Annual Average HHI",
       y = "Period Agggregate HHI") +
  theme_minimal()

tenyear.owner.permits %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S") %>% 
  ggplot() +
  geom_point(aes(x = AnnualAverageHHI, y = period.owner.tot.hhi)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(title = "(1990-2020) Annual Average HHI (x), Period Agggregate HHI (y)",
       x = "Annual Average HHI",
       y = "Period Agggregate HHI") +
  theme_minimal()

tenyear.owner.permits %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S") %>% 
  ggplot() +
  geom_point(aes(x = norm.period.hhi, y = period.owner.tot.hhi)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(title = "(1990-2020)",
       x = "Norm. Period Agggregate HHI",
       y = "Period Agggregate HHI") +
  theme_minimal()

tenyear.owner.permits %>% filter(substr(CFEC.Permit.Fishery,1,1)=="S", period==1) %>% 
  ggplot() +
  geom_point(aes(x = period.avg.hhi, y = norm.period.hhi)) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  labs(title = "(1990-2020)",
       x = "Annual Average HHI",
       y = "Norm. Period Agggregate HHI") +
  theme_minimal()


tenyear.owner.permits %>% mutate(cor.AA.PA = cor)
cor(tenyear.owner.permits$period.owner.tot.hhi, tenyear.owner.permits$AnnualAverageHHI)

#  summarise(hhi.deviation = first(hhi.deviation), rev.deviation = first(rev.deviation), period = first(period)) %>%
#  filter(!is.na(CFEC.Permit.Holder.Filing.Number))

rev.permits.changing %>% 
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  filter(any(is.shock.pp == 1)) %>% 
  filter(rev.deviation>0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  summarise(hhi.rev.cor = cor(hhi.deviation, rev.deviation)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue change and hhi change from mean", 
           title = "Correlation between HHI and Revenue Deviations (primary permit shocks) +")

rev.permits.changing %>% 
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  filter(any(is.shock.pp == 1)) %>% 
  filter(rev.deviation<=0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  summarise(hhi.rev.cor = cor(hhi.deviation, rev.deviation)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue change and hhi change from mean", 
           title = "Correlation between HHI and Revenue Deviations (primary permit shocks) -")

rev.permits.changing %>% 
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  filter(!any(is.shock.pp == 1)) %>% 
  filter(rev.deviation>0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  summarise(hhi.rev.cor = cor(hhi.deviation, rev.deviation)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue change and hhi change from mean", 
           title = "Correlation between HHI and Revenue Deviations (shocked non-primary permit) +")

rev.permits.changing %>% 
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  filter(!any(is.shock.pp == 1)) %>% 
  filter(rev.deviation<=0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  summarise(hhi.rev.cor = cor(hhi.deviation, rev.deviation)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue change and hhi change from mean", 
           title = "Correlation between HHI and Revenue Deviations (shocked non-primary permit) - ")


```

## Total Fishery-Wide Revenue CV

```{r HHI Deviations, echo=FALSE}
  fishery.rev <- permit.annual.rev %>% ungroup() %>% 
    group_by(Batch.Year, CFEC.Permit.Fishery) %>%
    summarise(fishery.annual.rev = sum(year.revenue, na.rm = TRUE), active_fishers = n_distinct(CFEC.Permit.Holder.Filing.Number)) %>% 
    filter(active_fishers!=1) %>% 
    mutate(period = floor((Batch.Year - 1991) / period_length) + 1)
  
  fishery.cv <- fishery.rev %>% 
    group_by(period, CFEC.Permit.Fishery) %>%
    summarise(fishery.cv = sd(fishery.annual.rev, na.rm = TRUE)/mean(fishery.annual.rev, na.rm = TRUE), 
           fishery.mean = mean(fishery.annual.rev, na.rm = TRUE), 
           mean.active.fishers = mean(active_fishers, na.rm = TRUE),
           num.years = n()) %>% 
    filter(period!=4)

rev.hhi.changing <- permit.annual.rev %>% ungroup() %>%
  group_by(Batch.Year, CFEC.Permit.Fishery, CFEC.Permit.Holder.Filing.Number) %>% 
  summarise(fishery.annual.rev = sum(year.revenue, na.rm = TRUE), period = floor((Batch.Year - 1991) / period_length) + 1) %>% 
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  mutate(owner.annual.rev = sum(fishery.annual.rev, na.rm = TRUE), rev.share = fishery.annual.rev/sum(fishery.annual.rev, na.rm = TRUE), owner.annual.hhi = sum(rev.share^2, na.rm = TRUE)) %>% 
  group_by(period, CFEC.Permit.Holder.Filing.Number) %>% 
  mutate(period.avg.rev = mean(owner.annual.rev, na.rm = TRUE), period.avg.hhi = mean(owner.annual.hhi, na.rm = TRUE)) %>% 
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  arrange(Batch.Year) %>% 
  mutate(hhi.deviation = owner.annual.hhi - period.avg.hhi, rev.deviation = (owner.annual.rev - period.avg.rev)/period.avg.rev) %>% # calculate change in hhi from the period mean
  summarise(hhi.deviation = first(hhi.deviation), rev.deviation = first(rev.deviation), period = first(period)) %>%
  filter(!is.na(CFEC.Permit.Holder.Filing.Number))
```

```{r HHI Deviation Plots}
rev.hhi.changing %>%
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  summarise(hhi.rev.cor = cor(hhi.deviation, rev.deviation)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue change and hhi change from mean", 
           title = "Correlation between HHI and Revenue Deviations")

rev.hhi.changing %>%
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  filter(rev.deviation<=0) %>% 
  summarise(hhi.rev.cor = cor(hhi.deviation, rev.deviation)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue change and hhi change from mean", 
           title = "Correlation between HHI and Negative Revenue Deviations")

rev.hhi.changing %>%
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  filter(rev.deviation>0) %>% 
  summarise(hhi.rev.cor = cor(hhi.deviation, rev.deviation)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue change and hhi change from mean", 
           title = "Correlation between HHI and Positive Revenue Deviations")
  

#cor(rev.hhi.changing$hhi.deviation, rev.hhi.changing$rev.deviation)
  
```
Goal of the next section is find the when fishing permit owners add a new fishery or leave a fishery and how that relates to revenue changes.
```{r Fishery_changes, echo=FALSE}
fishing.changes <- permit.annual.rev %>%
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number, CFEC.Permit.Fishery) %>%
  summarise(owner.annual.rev = sum(year.revenue, na.rm = TRUE)) %>%
  group_by(CFEC.Permit.Holder.Filing.Number, Batch.Year) %>%
  summarise(permit.list = list(unique(CFEC.Permit.Fishery)))

fishing.changes <- fishing.changes %>%
  group_by(CFEC.Permit.Holder.Filing.Number) %>%
  arrange(Batch.Year) %>%
  mutate(
    future.permit.list = lead(permit.list),
    past.permit.list = lag(permit.list),
    future.check = map2(permit.list, future.permit.list, ~ .x %in% .y),
    past.check = map2(permit.list, past.permit.list, ~ .x %in% .y)
  )
fishing.changes <- fishing.changes %>%
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  arrange(Batch.Year) %>% 
  mutate(lag.future.check = lag(future.check)) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, Batch.Year) %>% 
  mutate(num.new.permit = sum(!unlist(past.check), na.rm = TRUE), num.dropped.permit = sum(unlist(lapply(lag.future.check, function(x) if(is.null(x)) x else !x)), na.rm = TRUE)) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  mutate(start.flag = (Batch.Year==min(Batch.Year)))

joined.data <- fishing.changes %>% ungroup() %>% 
  left_join(rev.hhi.changing, join_by(Batch.Year, CFEC.Permit.Holder.Filing.Number)) %>% 
  left_join(test, join_by(Batch.Year, CFEC.Permit.Holder.Filing.Number))

joined.data %>% filter(!start.flag) %>% filter(hhi.deviation!=0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  summarise(hhi.rev.cor = cor(rev.deviation, num.dropped.permit)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue deviation and dropped permits", 
           title = "Correlation between Dropped Permits and Revenue Deviations")

joined.data %>% filter(!start.flag) %>% filter(hhi.deviation!=0) %>% 
  filter(rev.deviation>0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  summarise(hhi.rev.cor = cor(rev.deviation, num.dropped.permit)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue deviation and dropped permits", 
           title = "Correlation between Dropped Permits and Revenue (Positive) Deviations")

joined.data %>% filter(!start.flag) %>% filter(hhi.deviation!=0) %>% 
  filter(rev.deviation<0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  summarise(hhi.rev.cor = cor(rev.deviation, num.dropped.permit)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue deviation and dropped permits", 
           title = "Correlation between Dropped Permits and Revenue (Negative) Deviations")


##############


joined.data %>% filter(!start.flag) %>% filter(hhi.deviation!=0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  summarise(hhi.rev.cor = cor(rev.deviation, num.new.permit)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue deviation and new permits", 
           title = "Correlation between New Permits and Revenue Deviations")

joined.data %>% filter(!start.flag) %>% filter(hhi.deviation!=0) %>% 
  filter(rev.deviation>0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  summarise(hhi.rev.cor = cor(rev.deviation, num.new.permit)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue deviation and new permits", 
           title = "Correlation between NEW Permits and Revenue (Positive) Deviations")

joined.data %>% filter(!start.flag) %>% filter(hhi.deviation!=0) %>% 
  filter(rev.deviation<0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  summarise(hhi.rev.cor = cor(rev.deviation, num.new.permit)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue deviation and new permits", 
           title = "Correlation between New Permits and Revenue (Negative) Deviations")

```

```{r rolling average hhi}
test <- permit.annual.rev %>%
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  summarise(owner.annual.rev = sum(year.revenue, na.rm = TRUE)) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  arrange(Batch.Year) %>%
  mutate(income_avg = zoo::rollapply(owner.annual.rev, width = 6, FUN = mean, fill = NA)) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>%
  fill(income_avg, .direction = "up") %>% 
  fill(income_avg, .direction = "down")

test <- permit.annual.rev %>%
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number, CFEC.Permit.Fishery) %>% 
  summarise(owner.annual.rev = sum(year.revenue, na.rm = TRUE)) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number) %>% 
  arrange(Batch.Year) %>%
  mutate(income_avg = zoo::rollapply(owner.annual.rev, width = 6, FUN = mean, fill = NA))

```


```{r Fishery-wide CV plot, fig.width=14}

fishery.cv %>% ungroup() %>% 
  filter(period==1) %>%
    ggplot(aes(x=CFEC.Permit.Fishery, y=fishery.cv)) +
      geom_col()+
      labs(y="Fishery-Wide Revenue CV", 
           x = "Fishery (defined by the permit)", 
           title = "Fishery-Level CV Across Time, Period 1 (1991-2000)")+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))

fishery.cv %>% ungroup() %>% 
  filter(period==1) %>%
    ggplot(aes(x=CFEC.Permit.Fishery, y=fishery.cv)) +
      geom_col()+
      labs(y="Fishery-Wide Revenue CV", 
           x = "Fishery (defined by the permit)", 
           title = "Fishery-Level CV Across Time, Period 2 (2001-2010)")+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))

fishery.cv %>% ungroup() %>% 
  filter(period==1) %>%
    ggplot(aes(x=CFEC.Permit.Fishery, y=fishery.cv)) +
      geom_col()+
      labs(y="Fishery-Wide Revenue CV", 
           x = "Fishery (defined by the permit)", 
           title = "Fishery-Level CV Across Time, Period 3 (2011-2020)")+
      theme(axis.text.x = element_text(angle = 45, hjust = 1))

fishery.cv %>% ungroup() %>% filter(CFEC.Permit.Fishery!="S 04X" & CFEC.Permit.Fishery!="S 04F") %>% 
  ggplot(aes(x=CFEC.Permit.Fishery, y=fishery.cv, fill=factor(period))) +
  geom_col(position = "dodge") +
  labs(y="Fishery-Wide Revenue CV", 
       x = "Fishery (defined by the permit)", 
       title = "Fishery-Level CV Across Time",
       fill = "Period") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_discrete(labels = c("1991-2000", "2001-2010", "2011-2020"))
```
Want to know if it is a prime or secondary permit that is being hurt during a revenue shock

```{r summary plots}
rev.permits.changing %>% 
  group_by(Batch.Year, CFEC.Permit.Holder.Filing.Number) %>% 
  filter(!any(is.shock.pp == 1)) %>% 
  filter(rev.deviation<=0) %>% 
  group_by(CFEC.Permit.Holder.Filing.Number, period) %>% 
  summarise(hhi.rev.cor = cor(hhi.deviation, rev.deviation)) %>% 
  ungroup() %>%
    ggplot(aes(x = hhi.rev.cor)) +
      geom_histogram()+
      labs(y="count", 
           x = "owner-level correlation between revenue change and hhi change from mean", 
           title = "Correlation between HHI and Revenue Deviations (shocked non-primary permit) - ")
```


